Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-24 STA304 Term Paper 1/paper/paper.qmd
Add files via upload

---
title: "Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023"
subtitle: "Analyzing Theft and Assault Trends Across Neighborhoods "
author: 
  - Mingxuan Liu
thanks: "Code and data are available at: LINK."
date: 09-21-2024
date-format: long
abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different urban areas from 2014 to 2023. Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods. And crime in some areas continues to increase, while in others it fluctuates or decreases. In addition, it is worth noting that there is also a correlation between population size and assault rates. Based on the research results, this paper provides targeted management schemes and resource reallocation schemes for the government and law enforcement agencies to reduce the community crime rate."
format: pdf
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
bibliography: references.bib
---
```{r}
#| echo: false
#| warning: false
#### Preamble ####

>>>>

---
title: "Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023"
subtitle: "Analyzing Theft and Assault Trends Across Neighborhoods "
author: 
  - Mingxuan Liu
thanks: "Code and data are available at: https://github.com/MingxuanLiu506/Crime_Rate.git"
date: 09-21-2024
date-format: long
abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different urban areas from 2014 to 2023. Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods. And crime in some areas continues to increase, while in others it fluctuates or decreases. In addition, it is worth noting that there is also a correlation between population size and assault rates. Based on the research results, this paper provides targeted management schemes and resource reallocation schemes for the government and law enforcement agencies to reduce the community crime rate."
format: pdf
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
bibliography: references.bib
---
```{r}
#| echo: false
#| warning: false
#### Preamble ####
